% resume.tex
%
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
% (c) 2007-2014 Todd C. Miller <Todd.Miller@courtesan.com> http://www.courtesan.com/todd
%
% This work is licensed under the Creative Commons Attribution-ShareAlike 3.0 Unported License. To view a copy of this license, visit http://creativecommons.org/licenses/by-sa/3.0/ or send a letter to Creative Commons, 171 Second Street, Suite 300, San Francisco, California, 94105, USA.

\documentclass[letterpaper,10pt]{article}

%-----------------------------------------------------------
\usepackage[empty]{fullpage}
\usepackage{color}
\usepackage{enumerate}
\usepackage{hyperref}
\definecolor{mygrey}{gray}{0.90}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Adjust margins to 0.5in on all sides
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}
\renewcommand{\familydefault}{\sfdefault}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\large \colorbox{mygrey}{\begin{minipage}{\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[4]{%
  \item\textbf{#1} \hfill #2\null\\
  \textit{#3} \hfill \textit{#4}%
  \vspace{-5pt}
}%-----------------------------------------------------------

\begin{document}
\begin{center}
\textbf{\Huge Garrett Beatty} \\
\vspace{0.05in}
856-905-6074 $\bullet$ \href{mailto:beattyg2@tcnj.edu}{beattyg2@tcnj.edu} $\bullet$ \href{http://github.com/GarrettBeatty}{github.com/GarrettBeatty} $\bullet$ \href{http://linkedin.com/in/garrett-beatty}{linkedin.com/in/garrett-beatty} $\bullet$ \href{https://gbeatty.com}{gbeatty.com}
\end{center}

\vspace{-0.05in}

\resheading{Education}
\begin{itemize}

\ressubheading{The College of New Jersey}{Ewing, NJ}{Bachelor of Science in Computer Science}{Aug. 2015 - May 2019}
	\begin{itemize}
		\resitem{Advanced Courses: Natural Language Processing, High Performance Computing, Combinatorics}
		\resitem{Co-Founder/Vice President: TCNJ Table Tennis Club}
	\end{itemize}
\end{itemize}

\resheading{Work Experience}
\begin{itemize}
\ressubheading{Lockheed Martin}{Moorestown, NJ}{Software Engineering Intern}{Jun. 2018 - Aug. 2018}
	\begin{itemize}
		\resitem{Worked on an Agile team to support the development of the Aegis Combat System using Java and C++.}
		\resitem{Automated parts of the build process using Jenkins, Python, and Bash.}
		\resitem{Collaborated with a team of 6 interns to simulate a vehicle that can transport and fire a rocket at a target using MATLAB.}
	\end{itemize}	

\ressubheading{The College of New Jersey}{Ewing, NJ}{Student Researcher - Machine Learning (ML)}{Jan. 2017 - Dec. 2017}
	\begin{itemize}
		\resitem{Designed a machine learning infrastructure with a team of 5 students and faculty in Python using machine learning and statistical analysis libraries such as scikit-learn, numpy, pandas, and matplotlib.}
		\resitem{Improved the speed of the infrastructure by 95\% by adding support for parallel processing on the High Performance Cluster (HPC).}
		%\resitem{Researched and integrated active learning stopping methods into a machine learning infrastructure in order to reduce annotation cost within the Natural Language Processing (NLP) field.}
		\end{itemize}

\ressubheading{Comcast}{Philadelphia, PA}{Software Engineering Intern}{Jun. 2016 - Aug. 2016}
	\begin{itemize}
		\resitem{Increased the efficiency of the Quality Assurance team by creating a Node.js application that automatically generates unit testing reports, which can be filtered by date, device type, operating system, etc.}
		\resitem{Collaborated with another intern to create a web application in C\#, HTML, and Javascript that connects to an SQL database to retrieve customer session information.}
	\end{itemize}
\end{itemize}

\resheading{Projects}
\begin{itemize}

\ressubheading{Android Application - ``arXiv eXplorer"}{}{\href{http://arxiv.gbeatty.com}{arxiv.gbeatty.com}}{}
	\begin{itemize}
		\resitem{Published an Android application with over 1,000 downloads that allows users to browse, search, and download scientific papers from \href{http://arxiv.org}{arxiv.org}.}
		\resitem{Java, Butterknife, OkHttp, Sugar ORM, arXiv API, Travis CI, Fastlane}
	\end{itemize}
	
%\ressubheading{MPI Parallel Processing - ``Conway's Game of Life"}{}{\href{http://conway.gbeatty.com/}{conway.gbeatty.com}}{}
%	\begin{itemize}
%		\resitem{Utilized the Message Passing Interface (MPI) to parallelize ``Conway's Game of Life" in C.}
%		\resitem{C, MPI, SLURM}
%	\end{itemize}

\ressubheading{Photo Location Visualizer}{}{\href{http://photo.gbeatty.com}{photo.gbeatty.com}}{}
	\begin{itemize}
		\resitem{Created a web application that allows users to see their photos on Google Maps based on their geo-location metadata.}
		\resitem{Python, Flask, Heroku, Google Maps API, Google Picasa API}
	\end{itemize}


\ressubheading{RSS Feed Creator}{}{\href{http://rss.gbeatty.com/}{rss.gbeatty.com}}{}
	\begin{itemize}
		\resitem{Deployed a web application that allows users to easily view and manage their RSS feeds.}
		\resitem{Python, Flask, Postgres, Heroku, Travis CI}
	\end{itemize}

\end{itemize}

\resheading{Skills}
	\begin{itemize}
	\resitem{\textbf{Proficient:} Python, Java}
	\resitem{\textbf{Past Experience:} C, C++, C\#, SQL, Ruby, PHP, Node.js, Perl, Javascript, MATLAB, HTML, CSS, Jade, Bash}
	\resitem{\textbf{Tools:} Git, ClearCase, Jenkins, Travis CI, Postgres, MariaDB, Linux/UNIX, Heroku, SLURM, Fastlane}
	\resitem{\textbf{Libraries/Frameworks:} scikit-learn, numpy, pandas, matplotlib, Keras, OpenCV, Flask, Django, Robot Framework, Butterknife, OkHtttp}
	\end{itemize}

\resheading{Publications}
\begin{description}
\item[``Impact of Batch Size on Stopping Active Learning for Text Classification",]
\emph{Proceedings of the 2018 IEEE 12th International Conference on Semantic Computing (ICSC), Laguna Hills, CA, 2018.}
\end{description}
%\fi
\end{document}

\resheading{Activities}
	\begin{itemize}
	\resitem{\textbf{Co-Founder/Vice President:} TCNJ Table Tennis Club}
	\resitem{\textbf{Member:} TCNJ Association for Computing Machinery}
	\resitem{\textbf{Member:} TCNJ Chess Club}
	\end{itemize}
	
\resheading{Awards}
	\begin{itemize}
	\resitem{\textbf{CCSCNE Programming Contest:} 5th Place}
	\end{itemize}

\resheading{Second Languages}
	\begin{itemize}
	\resitem{\textbf{Intermediate:} American Sign Language}
	\end{itemize}

\end{document}
